Software Ticket Quality

### 2017-10-31 proposal/mprop.tex
Finish paper on data quality in context

>>>>

\textbf{Data Quality in Context}\cite{strong1997data}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the authors was to analyze data quality in different 
    organizations, observe data quality problem patterns as well as see 
    its implications.
  \item \textbf{What was the method?}
    They performed a qualitative analysis, examining 42 data quality projects 
    from 3 organizations. They collected data via interviews of data procedures,
    custodians, customers and managers. The authors analysed each project using
    the data quality dimensions as content analysis codes. 
  \item \textbf{What did they learn?}
    One thing that the authors learned is that representational data quality 
    dimensions are underlying causes of accessibility data quality problem 
    patterns. Also, they observed three underlying causes for users' complaints
    regarding data not supporting their tasks:
      \begin{itemize}
        \item incomplete data;
        \item inadequately defined or measured data;
        \item data that could not be appropriately aggregated.
      \end{itemize}
  \item \textbf{Relevance to our work}: this paper brings valuable insight into
    major data quality issues and patterns, information which we can apply in 
    our own research.
\end{itemize}
